Meta-analysis on sex in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-08-31 individual-cohorts/meta_analysis/meta-analysis_sex.Rmd
Freeze analysis

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_sex.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on sex',
                                          overwrite=TRUE)
```

@@

@@

### Combine cohorts
```{r DE.results.dlpfc.combine, fig.width=10, fig.height=50}
res = merge(res_dlpfc, mpp_dlpfc[,c("gene_id", "AveExpr")], by.x="row.names", by.y="gene_id")

>>>>

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_sex.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on sex',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

```{r plotma}

f = function(x){
  pmin(1, pmax(-1, x))
}

ggplot(mpp_acc, aes(AveExpr, f(logFC))) + geom_point() + theme_bw() + geom_smooth(method="loess")  + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5)) + ggtitle("mpp_acc")

ggplot(mpp_dlpfc, aes(AveExpr, f(logFC))) + geom_point() + theme_bw() + geom_smooth(method="loess")  + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5)) + ggtitle("mpp_dlpfc")

ggplot(hbcc_dsACC, aes(AveExpr, f(logFC))) + geom_point() + theme_bw() + geom_smooth(method="loess")  + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5)) + ggtitle("hbcc_dsACC")

ggplot(hbcc_dlpfc, aes(AveExpr, f(logFC))) + geom_point() + theme_bw() + geom_smooth(method="loess")  + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5)) + ggtitle("hbcc_dlpfc")
```

@@

### Combine cohorts
```{r DE.results.dlpfc.combine.MA}
res = merge(res_dlpfc, mpp_dlpfc[,c("gene_id", "AveExpr")], by.x="row.names", by.y="gene_id")

ggplot(res, aes(AveExpr, logFC)) + geom_point() + theme_bw() + geom_smooth(method="loess")  + theme(aspect.ratio=1)
```

```{r DE.results.dlpfc.hbcc.plot_sex_compare, fig.width=10, fig.height=50}
figList = plot_sex_compare(res)
plot_grid(plotlist=figList, ncol=2) 
```
